UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface

### 2022-08-14 main.tex
:pencil: Add introduction to UniScatter

	\begin{figure*}[!t]
		\subfloat[Block Diagram]{
			\resizebox{0.32\linewidth}{!}{
				\input{assets/illustration/block_diagram.tex}
			\label{fi:block_diagram}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.37\linewidth}{!}{
				\input{assets/illustration/equivalent_circuit.tex}
			\label{fi:equivalent_circuit}
		\subfloat[Scatter Model]{
			\resizebox{0.28\linewidth}{!}{
				\input{assets/illustration/scatter_model.tex}
			\label{fi:scatter_model}
		\caption{Block diagram, equivalent circuit, and scatter model of a passive backscatter node. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}

@@

@@

	% \begin{subsection}{Opportunities and Challenges}
	\begin{subsection}{Opportunities}
		We have seen conventional scattering applications as \gls{bc}, \gls{sr} and \gls{ris} using the reflection pattern \eqref{eq:reflection_pattern_antenna}, \eqref{eq:reflection_pattern_metamaterial} for either backscatter modulation \eqref{eq:backscatter_modulation} or passive beamforming \eqref{eq:passive_beamforming}.
		A natural but critical question is, for a given scatterer with pre-determined reflection pattern set, \emph{can we softly bridge backscatter modulation and passive beamforming by appropriate reflection design?}
		This question is answered in Section \ref{se:uniscatter}.
	\end{subsection}
\end{section}

\begin{section}{UniScatter}
	\begin{subsection}{UniScatter Nodes}
		% TODO compare BC, SR and IRS
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
			}
			\caption{
				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and UniScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter block, with guidance from input probability distribution.
			}
			\label{fi:uniscatter}
		\end{figure}
		% ! Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signals.
		% As shown in Fig. \subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
		% Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
		% When illuminated, the node absorbs a portion of the impinging wave for information decoding and/or energy harvesting \cite{Kim2021a}, and backscatters the remaining as \emph{structural} and \emph{antenna} components.
		% The former consistently contributes to environment multipath and can be modelled by channel estimation \cite{Boyer2014}, while the latter depends on antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
		% Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ states.

>>>>

@@

	% In this section, we first introduce the principles of two common scatterer categories, then briefly
	In this section, we first introduce two common scatterer categories and review their operation principles, then briefly discuss how scatterers realize backscatter modulation and channel reconfiguration over reflection patterns.

@@

	\begin{subsection}{Opportunities}
		We have seen conventional scattering applications as \gls{bc}, \gls{sr} and \gls{ris} using the reflection pattern \eqref{eq:reflection_pattern_antenna}, \eqref{eq:reflection_pattern_metamaterial} for either backscatter modulation \eqref{eq:backscatter_modulation} or passive beamforming \eqref{eq:passive_beamforming}.
		A natural but critical question is, for a given scatterer with pre-determined reflection pattern set, \emph{can we softly bridge backscatter modulation and passive beamforming by appropriate reflection design?}
		This question is answered in Section \ref{se:uniscatter}.
	\end{subsection}
\end{section}

\begin{section}{UniScatter}
	We introduce UniScatter as a novel low-power communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} using shared spectrum, energy and infrastructures.
	% In particular, the passive UniScatter nodes ride over an active legacy transmission to simultaneously encode self information and reconfigure wireless environment.
	% Using shared spectrum, energy and infrastructures, the passive UniScatter nodes ride over an active legacy transmission for backscatter modulation and passive beamforming, while the low-complexity cooperative UniScatter receiver decodes both links
	% In particular, the passive UniScatter nodes adapt input distribution based on link priority and \gls{csi}
	In particular, the passive UniScatter nodes ride over an active legacy transmission in a flexible and mutualistic manner, while the practical cooperative UniScatter receiver decodes both links under the benefits of backscatter modulation and passive beamforming.
	\begin{subsection}{UniScatter Nodes}
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fi:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fi:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fi:scatter_model}
			}
			\caption{Block diagram, equivalent circuit, and scatter model of a passive backscatter node. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
		\end{figure*}
		% TODO compare BC, SR and IRS
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
			}
			\caption{
				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and UniScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter block, with guidance from input probability distribution.
			}
			\label{fi:uniscatter}
		\end{figure}
		% ! antenna-based
		% ! Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signals.
		% As shown in Fig. \subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
		% Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
		% When illuminated, the node absorbs a portion of the impinging wave for information decoding and/or energy harvesting \cite{Kim2021a}, and backscatters the remaining as \emph{structural} and \emph{antenna} components.
		% The former consistently contributes to environment multipath and can be modelled by channel estimation \cite{Boyer2014}, while the latter depends on antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
		% Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ states.
